Improving Software Maintainability through Automated Refactoring of Code Clones

### 2020-04-26 ase/paper.tex
Updates from Overleaf

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such anti-patterns, the codebase should be refactored. Many tools aid in the detection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability. Moreover, manual code clone refactoring is often tedious and could benefit from an automated tool.

We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them using the ``Extract Method'' refactoring technique. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones would improve system design if refactored. We evaluate our approach over a large corpus of open-source Java projects.

>>>>

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. Several studies show however, that not all duplication should be refactored. When some duplication is refactored, other system attributes are negatively affected thus resulting in a negative impact on the codebase when all system attributes are considered. % To remove such anti-patterns, the codebase should be refactored. Many tools aid in the detection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability. Moreover, manual code clone refactoring is often tedious and could benefit from an automated tool.

We use software maintainabilty metrics to determine the impact of refactoring 
We consider the ``duplicate code'' code smell from a maintainability perspective. We analyze 
%We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones. We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them using the ``Extract Method'' refactoring technique. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones would improve system design if refactored. We evaluate our approach over a large corpus of open-source Java projects.
